
---
title: "Bootcamp R Workbook"
format: html
---


# Bootcamp Workbook

The purpose of this document is to assess and provide a framework to review the fundamentals of programming with R for Data Science.

# Task 1

Load in the tidyverse library and read in the following `.csv` file: ['https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-04-15/penguins.csv']()


```{r}

```

# Task 2

List the column names and view the imported data.
```{r}


```

# Task 3

Create a plot that shows the relationship between body mass and bill length
```{r}
  
```


# Task 4

Create a new dataframe/tibble that only has the body mass, bill length, and species and create a plot that shows the relationship between them

```{r}
```

# Task 5
Create a new column called body_mass_kg (Hint to convert grams to kilograms divide by 1000) and 
Create a boxplot that shows the ditribution of body mass in kilograms by island
```{r}
```

# Task 6 

Filter the data to only include Female penguins and plot flipper length by bill depth.
```{r}
```

# Task 7

Find and create a bar chart that shows the average body_mass by species.
(Hint you will need to remove nulls or use a similar argument in mean() use `mean()` to find the average)

```{r}
```

# Task 8 

Select one of the plots you created above and label the axises and give it a title.

```{r}
```
